Matching Bullets

### 2015-12-10 imaging-paper.Rnw
Correct a small warning issue

\begin{figure}[hbtp]
\centering
\begin{subfigure}[t]{\linewidth}
\caption{Groove detection for bullet 1-5 at a smoothing factor of 35.\label{fig:smoothfac1}}{%
<<smoothfac1, echo=FALSE, fig.width=7, fig.height=3, out.width='\\textwidth'>>=
get_grooves(br111_bullet, smoothfactor = 35, smoothplot = TRUE)$plot
@
    }
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
    \caption{Groove detection for bullet 1-5 at a smoothing factor of 5.\label{fig:smoothfac2}}{%
<<smoothfac2, echo=FALSE, fig.width=7, fig.height=3, out.width='\\textwidth'>>=
get_grooves(br111_bullet, smoothfactor = 5, smoothplot = TRUE)$plot
@
    }
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
    \caption{Groove detection for bullet 1-5 at a smoothing factor of 65.\label{fig:smoothfac3}}{%
<<smoothfac3, echo=FALSE, fig.width=7, fig.height=3, out.width='\\textwidth'>>=
get_grooves(br111_bullet, smoothfactor = 65, smoothplot = TRUE)$plot
@
    }
\end{subfigure}
\caption{\label{fig:varysmooth} Groove detection at smoothing factors of 35, 5, and 65 respectively. Note that a smoothing factor of 5 yields enough variation prior to the groove that the right groove is not detected properly, while a smoothing factor of 65 over-smoothes and causes the peak on the right to disappear, so that the peak and groove are both not detected properly.}
\end{figure}

>>>>

\begin{figure}[hbtp]
\centering
\begin{subfigure}[t]{\linewidth}
\caption{Groove detection for bullet 1-5 at a smoothing factor of 35.\label{fig:smoothfac1}}{%
<<smoothfac1, echo=FALSE, fig.width=7, fig.height=3, out.width='\\textwidth', warning=FALSE>>=
get_grooves(br111_bullet, smoothfactor = 35, smoothplot = TRUE)$plot
@
    }
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
    \caption{Groove detection for bullet 1-5 at a smoothing factor of 5.\label{fig:smoothfac2}}{%
<<smoothfac2, echo=FALSE, fig.width=7, fig.height=3, out.width='\\textwidth', warning=FALSE>>=
get_grooves(br111_bullet, smoothfactor = 5, smoothplot = TRUE)$plot
@
    }
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
    \caption{Groove detection for bullet 1-5 at a smoothing factor of 65.\label{fig:smoothfac3}}{%
<<smoothfac3, echo=FALSE, fig.width=7, fig.height=3, out.width='\\textwidth', warning=FALSE>>=
get_grooves(br111_bullet, smoothfactor = 65, smoothplot = TRUE)$plot
@
    }
\end{subfigure}
\caption{\label{fig:varysmooth} Groove detection at smoothing factors of 35, 5, and 65 respectively. Note that a smoothing factor of 5 yields enough variation prior to the groove that the right groove is not detected properly, while a smoothing factor of 65 over-smoothes and causes the peak on the right to disappear, so that the peak and groove are both not detected properly.}
\end{figure}
